Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-04-27 cav2017/cav2017.tex
+ stability for the synthesis specification

When mapping back to the notation used for describing the general
architecture of the program synthesizer, the controller $K$ denotes $P$ and
$(x_0, u_k)$ represents $a$.

>>>>

When mapping back to the notation used for describing the general
architecture of the program synthesizer, the controller $K$ denotes $P$,
$(x_0, u_k)$ represents $a$ and $\phi_{stability} \wedge \phi_{input} \wedge \phi_{init} \wedge \phi_{safety}$
denotes the specification $\sigma$.
